%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=black, linkcolor=black, citecolor=black]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemexp}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}




\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Ramachandra Yerramsetti}} & Email: \href{mailto:}{rcyerramsetti@protonmail.com}\\
  \href{https://rcyerramsetti.com/}{Portfolio: https://rcyerramsetti.com/} & \href{https://www.linkedin.com/in/ramachandra-yerramsetti/}LinkedIn/Ramachandra Yerramsetti\\

  \href{https://github.com/ramchandra3101}{Github: ~~github.com/ramchandra3101}& Mobile:~~~(959)-232-0757 \\
 \end{tabular*}
 
 
\section{Experience}

 \resumeSubHeadingListStart
 
       \resumeSubheading{Full Stack Engineer - UCONN Health }{Jan 2024 - Present}
    { UCONN School of Dental Medicine $|$ C\#, .NET,  Python, Django, React Native}{Farmington, CT}
    \resumeItemListStart
        \resumeItemexp {Spearheaded the development of a mobile app(\href{https://github.com/ramchandra3101/strip_frontend} striplens) using \textbf{React Native}, enhancing COVID-19 diagnostics accuracy by 95\% through real-time image processing and test line detection.}

          \resumeItemexp{Engineered \textbf{REST APIs} with \textbf{Node.js} and \textbf{FastAPI}, reducing \href{https://github.com/ramchandra3101/strip_backend} backend response time from 30s to 10s, and facilitating seamless communication between the mobile app and HPC server.}
          
          \resumeItemexp {Streamlined deployment using Docker, achieving a 50\% reduction in application downtime and improving scalability to handle over 1000 user requests per day}
          
          \resumeItemexp{Automated PCR thermocycler operations by creating a Python program that calls .NET functions, reducing human intervention by 100\%. Improved diagnostic workflow efficiency by 30\%.}
      \resumeItemListEnd

 
    \resumeSubheading{Senior Software Engineer -  SNCB- Belgian Train}{May 2022 - Jul 2023}
    {Tata Consultancy Services $|$ React.js, Express, Node.js, PostgreSQL }{Hyderabad, India}
    \resumeItemListStart
        \resumeItemexp
          {Implemented features for SNCB-NMBS  train ticket web app leveraging \textbf{React.js and Node.js serving over 4M users}. }
          \resumeItemexp
          {Designed scalable REST and GraphQL APIs using TypeScript, Node.js, Redis, and PostgreSQL.}
          \resumeItemexp{Architected an  \textbf{AS Java System} to deal with XML documents generated by 50+ SAP Systems, reducing security incidents by 40\%.}
      \resumeItemListEnd
      
    \resumeSubheading
		{Software Engineer  - Merck \& Co. }{July 2019 - April 2022}
		{Cognizant Technology Solutions. $|$ Javascript, React, Django, SQL, Oracle, Linux, Docker}{Chennai, India}
\resumeItemListStart
        \resumeItemexp{Developed a secure and  \textbf{scalable backend} for an ERP system using the  \textbf{Django framework (Python)}, significantly enhancing performance and scalability, while integrating \textbf{RESTful APIs} and third-party applications.}
         \resumeItemexp{ Converted design concepts and wireframes into intuitive application interfaces using HTML, CSS and ReactJS, following design patterns.}
        \resumeItemexp
          {Played a key role in attaining noteworthy enhancements in performance by identifying and remedying bottlenecks at both instance and database(MySQL) tiers, which led to substantial reductions in runtime for over 100 background jobs.}
        \resumeItemexp
          {Created a Python script to facilitate the smooth transfer of change objects from the development environment to testing, quality, and production environments.}
          
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5pt}
 
 \section{Techncal Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~ JavaScript, TypeScript, Python, C,  SQL, Bash(Linux, PowerShell)}
	\resumeSubItem{Web Dev}{~~~~~~~React, Vue, Node.JS, Express, Django, React Native}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~Terraform, Jenkins, Kubernetes, Docker, Git, GitHub, PostgreSQL, MySQL, SQLite, NoSQL(MongoDB)}
	\resumeSubItem{Cloud}{~~~~~~~~~~~~AWS: S3, ECS, CDK $|$ GCP: Kubernetes Engine, Container Registry $|$ Azure: App Service}
	\resumeSubItem{Devops}{~~~~~~~~~~Infrastructure as Code(IaC), Continous Integration and Deployment(CI/CD)}
	\resumeSubItem{Certifications}{~\href{https://www.credly.com/badges/f21dec56-8b41-499a-aebb-342a8c0dbf45/linked_in_profile}AWS Certified Cloud Practitioner(Issued 2024)}
\resumeSubHeadingListEnd

\vspace{-5pt}


%-----------PROJECTS-----------------

\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Citi bike usage prediction at Manhattan-NYC}{Implemented an \textbf{RNN(LSTM+GRU)} model for predicting Citi bike Usage in Manhattan with \textbf{83\%} accuracy. Awarded 1st prize in the Cyberinfrastructure competition organized by the National Science Foundation(NSF) for Best ML Model and Analysis. (Jan 2024)}
\vspace{2pt}
\resumeSubItem{E-Commerce Website for Clothing}{Designed a website for the KLAD clothing store using ReactJS for the front end and Node.js with Express for the back end. Integrated Axios for communication and utilized Mongoose to connect MongoDB.  (Sept 2023)}
\vspace{2pt}
\resumeSubItem{Predicting NFL outcomes based on Madden ratings}{Developed a Python-driven ML model for predicting NFL game outcomes using datasets spanning the last 20 years. Enhanced model accuracy by 40\% by integrating curated datasets, with a specific focus on player injury information.(Oct 2023)}
\vspace{2pt}
\resumeSubItem{Real-time chat Application}{Real-time chat application using Node and React Native, leveraging \textbf{Websockets} for instant communication.Utilized \textbf{Redis} for efficient storage.(June 2023). }




%-----------EDUCATION-----------------
\section{Education}
    \resumeSubheading
      {University of Connecticut}{August 2023 - May 2025}
      {Master of Engineering- Computer Science and Engineering;  GPA: 3.45/4.00}{Storrs, CT}
      \vspace{5pt}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Algorithms \& Complexity, Machine learning, Big Data Analytics, Data Mining}}}
       \resumeSubheading
      {K L University }{August 2015- May 2019}
      {Bachelor of Engineering- Electrical and Electronics Engineering;  GPA: 9.00/10.00}{Vijayawada, India}
      \vspace{5pt}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Object-Oriented programming(Java), Computer Organization and Architecture, C \& Data Structures }}} 
      
  
    
    
	    






%\vspace{2pt}
%\resumeSubItem{Drag-n-drop machine learning learning environment (Web Development, Machine Learning)}{Scratch like tool for implementing machine learning pipelines along with built in tutorial for each concept. Tech: Python, JavaScript (September '18)}
%\vspace{2pt}
%\resumeSubItem{Search Engine and Social Network(Web Development, Web Crawler, Search)}{Created from scratch a social network and a search engine based on the idea of integrating Facebook and Google. The launched website was among top 1000 websites in India during 2012-2013. Tech: PHP, MySQL, HTML, CSS, WebSockets, JavaScript, RSS, XML ( May '12)}
%\resumeSubHeadingListEnd
%\vspace{-5pt}
%\section{Publications}
%\resumeSubHeadingListStart
%\resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
%\vspace{2pt}
%\resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
\resumeSubHeadingListEnd

\vspace{-5pt}


%%-----------Awards-----------------
%\section{Honors and Awards}
%\begin{description}[font=$\bullet$]
%\item {Awarded title of Intel Software Innovator - May, 2019}
%\vspace{-5pt}
%\item {Second Runner's Up at TCS EngiNx Engineering Project Innovation Content - September, 2018 }
%\vspace{-5pt}
%\item {Runner's Up at Facebook Developers Circle Hackathon - August, 2017}

%\end{description}

%\vspace{-5pt}
%\section{Volunteer Experience}
%  \resumeSubHeadingListStart
%	\resumeSubheading
   % {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
  %  {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
%\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
 %   \resumeSubheading
  %  {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
  %  {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}

%\resumeSubHeadingListEnd

\end{document}